### 2018-02-24 DASFAA_2018/CR/Gruba_final/03-fe.tex

\begin{definition}
\label{def:lexi}
A lexicon $L$ consists of a set of topics $t$ such that each topic is associated with a set of cell words $c$, in which each cell word depicts an aspect of the topic.
\end{definition}

@@

In  \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user $u$ versus each topic $t$ in lexicon $sim(u, t)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.

System \sys{} employs a well established lexicon to discover the explicit interests of users.
%In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA %\cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector %\cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency) \cite{IEEEexample:books/cu/LeskovecRU14}, and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.

@@

The similarity of $b$ with a lexicon topic $t$ is defined as
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j).
\end{equation}

@@

If $sim(b, t)$ satisfies a certain threshold (3 by default), topic $t$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (Definition \ref{def:inte}).

\stitle{Step 3:}. If the $sim(b, t)$ in {\bf Step 2} cannot meet the threshold, i.e., explicit interest discovery over user $u$ fails, the implicit interests of user $u$ are further mined, by running the following steps 3.1$\&$3.2 in parallel.

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $|b_i|$ appears.
Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

TF-IDF based similarity is then calculated.
%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
%\begin{equation}
%\label{eq:sim-tf1}
%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
%\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}.
Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
where $N_t$ is the number of words in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = VEC_{W_f} \cdot VEC_t, where
\end{equation}
\begin{equation}
\label{eq:sum-tf1}
VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i], and
\end{equation}
\begin{equation}
\label{eq:sum-lexion}
VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j].
\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.

@@

\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is :
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t),
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.

\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
Such computation further extends to all the microblogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0, s_1, \ldots,\ s_{n-1}),
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k).
\end{equation}

>>>>

\begin{definition}
\label{def:lexi}
A lexicon $L$ consists of a set of topics $\gamma$ such that each topic is associated with a set of cell words $c$, in which each cell word depicts an aspect of the topic.
\end{definition}

@@

In  \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity $sim(w, c)$ of a word pair ($w$, $c$) could be generalized to the similarity of a microblog against one topic $sim(b, \gamma)$, and finally to a user $u$ versus each topic $\gamma$ in lexicon $sim(u, \gamma)$; topics with similarity satisfying certain thresholds are allocated to user $u$ and constitute the interests of $u$.

System \sys{} employs a well established lexicon to discover the explicit interests of users.
%In case when no proper explicit interests are found, TF-IDF (Term-Frequency and Inverse Document-Frequency) and Twitter-LDA %\cite{IEEEexample:zhao2011comparing} are leveraged to explore the implicit interests, during which word2vector %\cite{IEEEexample:mikolov2013distributed} is adopted to measure the similarity between two words.
When no proper explicit interests are found, two algorithms are leveraged to identify implicit interests: (1) TF-IDF (Term-Frequency and Inverse Document-Frequency), and (2) Twitter-LDA \cite{IEEEexample:zhao2011comparing} (a method to discover topics from Twitter, by applying the standard Latent Dirichlet Allocation (LDA) model \cite{IEEEexample:conf/jmlr/Blei03}), both of which adopt word2vector \cite{IEEEexample:mikolov2013distributed} to measure word similarity.

@@

The similarity of $b$ with a lexicon topic $\gamma$ is defined as
\begin{equation}
\label{eq:bt}
sim(b, \gamma) = \sum_{\substack{i, j}} sim(w_i, c_j).
\end{equation}

@@

If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $\gamma$.
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

\stitle{Step 3:}. If the $sim(b, \gamma)$ in {\bf Step 2} cannot meet the threshold, i.e., explicit interest discovery over user $u$ fails, the implicit interests of user $u$ are further mined, by running the following steps 3.1$\&$3.2 in parallel.

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $w_i$ appears.
Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

TF-IDF based similarity is then calculated.
%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
%\begin{equation}
%\label{eq:sim-tf1}
%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
%\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
For example, the similarity of $W_f$ over a single topic $\gamma$ in lexicon, written as $sim(W_f, \gamma)$, is defined as formula \ref{eq:sim-tf1}.
Here $W_f = \{(w_i, p_i)\}$, $\gamma = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
where $N_{\gamma}$ is the number of words in topic $\gamma$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, \gamma) = VEC_{W_f} \cdot VEC_t, where
\end{equation}
\begin{equation}
\label{eq:sum-tf1}
VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i], and
\end{equation}
\begin{equation}
\label{eq:sum-lexion}
VEC_t = \sum_{\substack{j}} \frac{1}{N_{\gamma}}*vec[c_j].
\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.

@@

\stitle{Step 4:} Hence, the similarity of a microblog $b$ against a lexicon topic $\gamma$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, \gamma) = \alpha * sim(W_f, \gamma) + (1 - \alpha) * sim(W_t, \gamma),
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.

\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall {\gamma}_k \in L$ results one similarity value of $sim(b, {\gamma}_k)$.
Such computation further extends to all the microblogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{\gamma\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0, s_1, \ldots,\ s_{n-1}),
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic ${\gamma}_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, {\gamma}_k).
\end{equation}

### 2018-02-24 DASFAA_2018/CR/Gruba_final/05-gm.tex

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
\end{equation}

We use accuracy to test results of using various $\alpha$ values. Suppose the label set we manually labeled for each microblog is $A$, the label set our method labeled is $B$.
The accuracy can be defined as:
\begin{equation}
\label{eq:def-accuracy}
accuracy = \frac{ A \cap B }{ A \cup B }
\end{equation}

To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0. So the accuracy can be defined as:

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
\end{equation}

>>>>

\begin{equation}
\label{eq:def-precision1}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
\end{equation}
